\textbf{Computational Fuzzy Extractors}

### 2013-05-15 CompFuzzExt.tex
write the talk abstract; edited Section 3

\newcommand{\class}[1]{{\ensuremath{\mathsf{#1}}}}
\newcommand{\gen}{\ensuremath{\class{Gen}}\xspace}
\newcommand{\rep}{\ensuremath{\class{Rep}}\xspace}
\newcommand{\sketch}{\ensuremath{\class{SS}}\xspace}
\newcommand{\rec}{\ensuremath{\class{Rec}}\xspace}
\newcommand{\enc}{\ensuremath{\class{Enc}}\xspace}
\newcommand{\dec}{\ensuremath{\class{Dec}}\xspace}
\newcommand{\prg}{\ensuremath{\class{prg}}\xspace}
\newcommand{\zo}{\ensuremath{\{0, 1\}}}
\newcommand{\vect}[1]{\ensuremath{\textbf{#1}}}
\newcommand{\zq}{\ensuremath{\mathbb{Z}_q}}
\newcommand{\Fq}{\ensuremath{\mathbb{F}_q}}
\newcommand{\sample}{\ensuremath{\class{Sample}}\xspace}
\newcommand{\neigh}{\ensuremath{\class{Neigh}}\xspace}
\newcommand{\dis}{\ensuremath{\mathsf{dis}}}

\newcommand{\A}{\mathcal{A}}
\newcommand{\D}{\mathcal{D}}

@@

%We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp. unpredictability) entropy when given a source with $m$ bits of entropy.  
In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.  In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $\log |\mathcal{M}| - \log |B_t(\cdot)|$.  Random linear codes~(in the Hamming metric) already achieve min-entropy $\log |\mathcal{M}|(1-o(1)) - \log B_t(\cdot)$ on uniform inputs, so it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.\bnote{I changed this bound to be size of metric space before it was just n which was wrong.  Do we prefer $n\log Z$?}  In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.

@@

We review definitions of Shannon codes~\cite{shannon1949mathematical}:
\begin{definition}
\label{def:shannon-code}
Let $\mathcal{C}$ be a set over space $\mathcal{M}$.  We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\neigh(c, t')) \neq c]<\epsilon$. To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
\end{definition}
This is a slightly stronger formulation than usual, in that we require the code to correct random errors of every size $t'<t$\footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compared to the volume of the ball of size $t$.  For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.  However, we work with an arbitrary recover functionality that is not necessarily monotone.}.

@@

%It is known (see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein) that, 
For the Hamming metric, any Shannon code (as defined in Definition~\ref{def:shannon-code}) can be converted into an information-theoretic secure sketch~(as described in \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein).  The idea is to use the code offset construction, and convert worst-case errors to random errors by randomizing the order of the bits of $w$ first, via a randomly chosen  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$). The formal statement is in the following Lemma.\bnote{I feel we should cite this.}
\begin{lemma}
\label{lem:shannon to sketch}
For an alphabet $Z$, let $\mathcal{C}$ over $Z^n$ be a $(t, \delta)$ Shannon code.  % with recovery procedure $\rec'$.
%  Let $W$ be a distribution with $\Hoo(W)\geq k$. 
%
% Define the following procedures
%\lnote{I think this description is buggy}
%\begin{center}
%\begin{tabular}{c|c}
%\begin{minipage}{3in}
%\textbf{\sketch}
%\begin{enumerate}
%\item Input $w\leftarrow W$.
%\item Sample $\pi$ from the space of all permutations from $\pi: [n]\rightarrow [n]$.
%\item Sample $c\leftarrow \mathcal{C}$.
%\item Apply $\pi$ bitwise to get $x_i = w_{\pi(i)}$.
%\item Output $p = x \oplus c, \pi$.
%\end{enumerate}
% \end{minipage} &
%\begin{minipage}{3in}
%\textbf{\rec}
%\begin{enumerate}
%\item Input $(w', p, \pi)$
%\item Apply $\pi^{-1}$ bitwise to get $x_i' = w_{\pi(i)}$.
%\item Compute $c' = p \oplus x'$.
%\item Compute $c = \rec'(c)$.
%\item Output $p\oplus c$.
%\\
%\end{enumerate}
%\end{minipage} 
%\end{tabular}
%\end{center}
Then there exists a $(Z^n, m, m-(n\log|Z|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $Z^n$. 
%satisfies the following properties~(probability over the choice of $\pi$ in $\sketch$):
%\begin{itemize}
%\item Correctness: $\forall w, w'$ where $dis(w, w')\leq t$, $\Pr[\rec(w', \sketch(w))\neq w]<\epsilon$.
%\item Security: $\Hav(W |\sketch(W)) \geq \Hoo(W) - (n-\log |C|)$.
%\item Efficiency: $\sketch$ is efficient if sampling from $C$ is efficient and $\rec$ is efficient if $\rec'$ is efficient.
%\end{itemize}
\end{lemma}
%\begin{construction}
%Let $\delta >0$ be a parameter.
%Let $C$ be a $(t, \epsilon)$ Shannon code over $\{0,1\}^n$.  Choose a permutation $\pi:\mathcal{M}rightarrow \mathcal{M}$ that is $\beta$-almost independent $\ell = \delta n/\log(n)$-wise permutation.  Thefn for $\beta = 2^{-\ell}
%\end{construction}
Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives us the negative result for the Hamming metric: a HILL-entropy secure sketch (for the uniform distribution) implies an information-theoretic one with similar parameters:
\begin{corollary}
\label{cor:rec yields sketch}
Let $Z$ be an alphabet. Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
If $s_{sec}\geq t(s_{rec} + n\log |Z|)$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
$4(\epsilon+t\delta)$. 
%Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  If no $(t, \epsilon)$-average error Shannon code over $\mathcal{M}$ exists of size $2^k$ then, $\forall (s_{rec}, t)$ recovery procedures $(\sketch, \rec)$ $H^{\hill}_{\epsilon, s}(X|\sketch(X))\not\geq k$ for $s=O(s_{rec}+s_{neigh})$.
\end{corollary}
\textbf{Notes:} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.

@@

\subsection{Bounds on Secure Sketches using Unpredictability Entropy}
\label{sec:imp unp sketch}
In the previous section, we showed that any sketch that retained HILL entropy could be transformed into an information theoretic sketch.  A reasonable question to ask is whether a sketch could retain unpredictability of the source.  We begin by defining conditional unpredictability entropy:

\begin{definition}~\cite[Definition 7]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{def:unp entropy}
For a distribution $(W, S)$, we say that $W$ has \emph{unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a collection of distributions $X_s$ (giving rise to a joint distribution $(X, S)$) such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, S))\leq \epsilon$, and for all circuits $\mathcal{I}$ of size $s_{sec}$,
\[
\Pr[\mathcal{I}(Z) = Y ] \leq 2^{-k}
.\]
\end{definition}
We will say a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch} with the security requirement replaced with $H^{\unp}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.  
We consider this notion to be a natural notion for a computational sketch as it can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}):
\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{lem:unp extraction} 
\bnote{We can't use the letter $C$ its taken for a distribution of codewords.}\bnote{We also $D$ as a distinguisher elsewhere.}
Let $W$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(W|S)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.  Then $\delta^{\mathcal{D}_{s'}}((\rext(W, U_d), S), U_m\times U_d\times S)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
\end{lemma}
Thus, if a sketch retained unpredictability entropy we could build a computational fuzzy extractor~(using the construction in \lemref{lem:fuzzy ext construction}).  
Unfortunately, the unpredictability entropy conditioned on the sketch must decrease as $t$ increases.  
%An adversaries ability to predict the output of the \rec algorithm increases with as $t$ grows.  %That is, $\forall Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)) , (Y, \sketch(W))$ our ability to predict $Y$ increases as $|B_t(\cdot)|$ increases.  
The formal statement is below:
\bnote{Should we list the stronger statement in the appendix or keep this for clarity?}
\begin{theorem}
\label{thm:imp of unp entropy}
Let $W$ be a distribution over $Z^n$ and let $(\sketch, \rec)$ be an unpredictability-entropy \\$(Z^n, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  If $s_{sec} \geq t(|\rec|+n\log |Z|)$, then $\tilde{m}\leq n\log |Z| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
\end{theorem}
This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.  The main difference with \thref{thm:impSketchArbitraryW} is that it is unknown if the indistinguishable distribution contains many points.  This means we cannot construct a good code out of the points of $Y$.  In \secref{sec:proof of imp unp entropy}, we prove a stronger theorem for larger class of metric spaces and for a relaxed notion of unpredictability entropy~(similar to the relaxed notion of HILL entropy in \defref{def:relaxed hill}).%Our bound is a result of the Hamming bound for the space.

@@

The lower bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} are strongest for high entropy sources.  The results get weaker as we consider sources with lower starter entropy.  This is necessary, if a source contains only codewords (of an error correcting code), no sketch is necessary.  This means we cannot rule out computational sketches for other arbitrary lower entropy distributions.  This same situation occurs when considering lower bounds for information-theoretic sketches.

@@

In this section we describe our main construction.  In this section, we consider only a uniform source $W$, we consider other distributions in \secref{sec:LWE block fixing sources}.  Our construction uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.   Let $\mathcal{I}_t$ be an algorithm that decodes a random linear code with at most $t$ errors.  We provide an informal description below.
\bnote{$\mathcal{I}$ is overloaded as the inverter in unpredictability entropy.  We okay?}
%Please refer to \consref{cons:informal construction} for the description of the construction.

\begin{construction}
Let $n$ be a security parameter and let $m> n$.  %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
Define $\gen, \rep$ as follows:%The following construction is a computational secure sketch:
%Code-offset construction of a secure sketch using a random linear code over a finite field $\Fq$. $\mathcal{I}_t (\vA, \vect{D})$ denotes an algorithm that decodes up to $t$ errors, i.e., an algorithm that finds $X'\in \Fq^n$ such that $\vect{A}X'$ is of Hamming distance at most $t$ from $\vect{D}$. $m > n$ are parameters to be figured out later.
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w\leftarrow W$ (where $W$ is some distribution over $\Fq^m$).
\item Sample $\vA\in\Fq^{m\times n}, X\in\Fq^n$ uniformly.
\item Compute $p = (\vA, \vA X+w)$, \\\ $r = X_{1,...,n/2}$.
\item Output $(r, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rec}
\begin{enumerate}
\item \underline{Input}: $(w', p)$ (where the Hamming distance between $w'$ and $w$ is at most $t$).
\item Parse $p$ as $(\vA, \vect{C})$; let $\vect{D}=\vect{C}-w'$.
\item Let $X = \mathcal{I}_t(\vA, \vect{D})$\\
\item Output $r = X_{1,...,n/2}$.
\end{enumerate}
\end{minipage} 
\end{tabular}
\end{center}
\label{cons:informal construction}
\end{construction}

Intuitively, security comes from the computational hardness of decoding random linear codes from a high number of errors (introduced by $w$).  
In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $\delta^{\mathcal{D}_{s_{sec}}}((X_{1,..., n/2},P), (U_{n/2 \log q}, P))\leq \epsilon$.  Furthermore, this construction is only useful if $\mathcal{I}_t$ can be efficiently implemented.  We demonstrate an efficient $\mathcal{I}_t$ that corrects a super-polynomial number of error patterns in polynomial time.

@@

We cannot immediately adapt the construction in \consref{cons:informal construction} to the $\LWE$ problem.  Standard formulations of $\LWE$ require the error term to come from the discretized Gaussian distribution.  
%\subsection{LWE with uniform errors}
%\label{subsec:LWE uniform error}
Recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$ with the uniform distribution over an interval reduces to the security of $\LWE$ where the noise comes from the discretized Gaussian\footnote{Micciancio and Peikert provide a similar formulation in~\cite{micciancio2013hardness}.  The result D\"{o}ttling and M\"{u}ller-Quade provides better parameters for our setting.}.  This allows us to directly encode $w$ as the error term in an $\LWE$ problem by splitting it  into $m$ blocks.  The size of these blocks is dictated by the following result of D\"{o}ttling and M\"{u}ller-Quade:
%As stated above this has two advantages for Construction~\ref{cons:LWESecureSketch}: 1) the bits of $W$ can be used directly and \rep can output $w$ instead of $sam_w$ 2) there is a fixed number of bits required to sample each dimension.  
%We present the formulation of D\"{o}ttling and M\"{u}ller-Quade: 
%\begin{lemma}~\protect{~\cite[Theorem 5]{dottling2012}}
%\label{lem:uniform LWE}
%Let $n$ be a security parameter.  Let $q = q(n))$ and $m = m(n) = \poly(n)$ be integers.  Let $\rho = \rho(n) \in (0,1)$ be such that $\rho q\geq 2n^2m$.  Assume there exists a PPT-algorithm that solves the LWE decision problem where $\vA,X$ are drawn uniformly at random and $E$ is drawn from the interval $[-\rho q, \rho q]$ with non-negligible probability.  Then there exists an efficient quantum-algorithm that approximates the decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) to within $\tilde{O}(n^{5/2}m/\rho)$ in the worst case.
%\end{lemma}

>>>>

\newcommand{\class}[1]{{\ensuremath{\mathsf{#1}}}}
\newcommand{\gen}{\ensuremath{\class{Gen}}\xspace}
\newcommand{\rep}{\ensuremath{\class{Rep}}\xspace}
\newcommand{\sketch}{\ensuremath{\class{SS}}\xspace}
\newcommand{\rec}{\ensuremath{\class{Rec}}\xspace}
\newcommand{\enc}{\ensuremath{\class{Enc}}\xspace}
\newcommand{\dec}{\ensuremath{\class{Dec}}\xspace}
\newcommand{\prg}{\ensuremath{\class{prg}}\xspace}
\newcommand{\zo}{\ensuremath{\{0, 1\}}}
\newcommand{\vect}[1]{\ensuremath{\textbf{#1}}}
\newcommand{\zq}{\ensuremath{\mathbb{Z}_q}}
\newcommand{\Fq}{\ensuremath{\mathbb{F}_q}}
\newcommand{\sample}{\ensuremath{\class{Sample}}\xspace}
\newcommand{\neigh}{\ensuremath{\class{Neigh}}\xspace}
\newcommand{\dis}{\ensuremath{\mathsf{dis}}}
\newcommand{\decode}{\ensuremath{\mathsf{Decode}}}

\newcommand{\A}{\mathcal{A}}

@@

%We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp. unpredictability) entropy when given a source with $m$ bits of entropy.  
In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.  In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $\log |\mathcal{M}| - \log |B_t(\cdot)|$.  Random linear codes~(in the Hamming metric) already achieve min-entropy $\log |\mathcal{M}|(1-o(1)) - \log B_t(\cdot)$ on uniform inputs\lnote{this point is confusing -- it's not the random linear codes, it's some construction applied to them in order to get a sketch -- we should cite appropriately and explain more clearly here and in 3.2}, so it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.\bnote{I changed this bound to be size of metric space before it was just n which was wrong.  Do we prefer $n\log Z$?} \lnote{I think your change is fine}  In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.

@@

We review definitions of Shannon codes~\cite{shannon1949mathematical}:
\begin{definition}
\label{def:shannon-code}
Let $\mathcal{C}$ be a set over space $\mathcal{M}$.  We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\neigh(c, t')) \neq c]<\epsilon$. To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
\end{definition}
This is a slightly stronger formulation than usual, in that for every size  $t'<t$ we require the code to correct $t'$ random errors \footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compared to the volume of the ball of size $t$.  For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.  However, we work with an arbitrary recover functionality that is not necessarily monotone.}.

@@

%It is known (see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein) that, 
For the Hamming metric, any Shannon code (as defined in Definition~\ref{def:shannon-code}) can be converted into an information-theoretic secure sketch~(as described in \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein).  The idea is to use the code offset construction, and convert worst-case errors to random errors by randomizing the order of the bits of $w$ first, via a randomly chosen  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$). The formal statement is in the following Lemma.\bnote{I feel we should cite this.}\lnote{You mean, say Lemma~\ref{lem:shannon to sketch} instead?  No problem if you want to.}
\begin{lemma}
\label{lem:shannon to sketch}
For an alphabet $Z$, let $\mathcal{C}$ over $Z^n$ be a $(t, \delta)$ Shannon code.  % with recovery procedure $\rec'$.
%  Let $W$ be a distribution with $\Hoo(W)\geq k$. 
%
% Define the following procedures
%\lnote{I think this description is buggy}
%\begin{center}
%\begin{tabular}{c|c}
%\begin{minipage}{3in}
%\textbf{\sketch}
%\begin{enumerate}
%\item Input $w\leftarrow W$.
%\item Sample $\pi$ from the space of all permutations from $\pi: [n]\rightarrow [n]$.
%\item Sample $c\leftarrow \mathcal{C}$.
%\item Apply $\pi$ bitwise to get $x_i = w_{\pi(i)}$.
%\item Output $p = x \oplus c, \pi$.
%\end{enumerate}
% \end{minipage} &
%\begin{minipage}{3in}
%\textbf{\rec}
%\begin{enumerate}
%\item Input $(w', p, \pi)$
%\item Apply $\pi^{-1}$ bitwise to get $x_i' = w_{\pi(i)}$.
%\item Compute $c' = p \oplus x'$.
%\item Compute $c = \rec'(c)$.
%\item Output $p\oplus c$.
%\\
%\end{enumerate}
%\end{minipage} 
%\end{tabular}
%\end{center}
Then there exists a $(Z^n, m, m-(n\log|Z|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $Z^n$. 
%satisfies the following properties~(probability over the choice of $\pi$ in $\sketch$):
%\begin{itemize}
%\item Correctness: $\forall w, w'$ where $dis(w, w')\leq t$, $\Pr[\rec(w', \sketch(w))\neq w]<\epsilon$.
%\item Security: $\Hav(W |\sketch(W)) \geq \Hoo(W) - (n-\log |C|)$.
%\item Efficiency: $\sketch$ is efficient if sampling from $C$ is efficient and $\rec$ is efficient if $\rec'$ is efficient.
%\end{itemize}
\end{lemma}
%\begin{construction}
%Let $\delta >0$ be a parameter.
%Let $C$ be a $(t, \epsilon)$ Shannon code over $\{0,1\}^n$.  Choose a permutation $\pi:\mathcal{M}rightarrow \mathcal{M}$ that is $\beta$-almost independent $\ell = \delta n/\log(n)$-wise permutation.  Thefn for $\beta = 2^{-\ell}
%\end{construction}
Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives us the negative result for the Hamming metric: a HILL-entropy secure sketch (for the uniform distribution) implies an information-theoretic one with similar parameters:
\begin{corollary}
\label{cor:rec yields sketch}
Let $Z$ be an alphabet. Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
If $s_{sec}\geq t(s_{rec} + n\log |Z|)$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
$4(\epsilon+t\delta)$. 
%Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  If no $(t, \epsilon)$-average error Shannon code over $\mathcal{M}$ exists of size $2^k$ then, $\forall (s_{rec}, t)$ recovery procedures $(\sketch, \rec)$ $H^{\hill}_{\epsilon, s}(X|\sketch(X))\not\geq k$ for $s=O(s_{rec}+s_{neigh})$.
\end{corollary}
\textbf{Notes:} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.

@@

\subsection{Bounds on Secure Sketches using Unpredictability Entropy}
\label{sec:imp unp sketch}
In the previous section, we showed that any sketch that retained HILL entropy could be transformed into an information theoretic sketch.  However, HILL entropy is a strong notion.  In this section, we therefore ask whether it is useful to consider a sketch that satisfies a minimal requirement: the value of the input is computationally hard to guess given the sketch.  We begin by recalling the definition of conditional unpredictability entropy, which captures the notion of ``hard to guess'' (we relax it similar to the way conditional HILL entropy was relaxed in the previous section).

\begin{definition}~\cite[Definition 7]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{def:unp entropy}
Let  $(W, S)$ be a pair of random variables. We say that $W$ has \emph{unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a pair of distributions $(X, Y)$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, Y))\leq \epsilon$, and for all circuits $\mathcal{I}$ of size $s_{sec}$,
\[
\Pr[\mathcal{I}(Y) = X ] \leq 2^{-k}
.\]
\end{definition}

We will say that a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-
hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\unp}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.  
Note this notion is quite natural: combining such a secure sketch via  \lemref{lem:fuzzy ext construction} with a particular type of extractor (called a 
\emph{reconstructive}~\cite{barak-computational}), would yield a computational fuzzy extractor (per \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).

Unfortunately, the conditional unpredictability entropy $\tilde{m}$ must decrease as $t$ increases, as the following theorem states.  (The proof of the theorem, generalized to more metric spaces, is in \secref{sec:proof of imp unp entropy}.)

\begin{theorem}
\label{thm:imp of unp entropy}
Let $Z$ be an alphabet $(\sketch, \rec)$ be an unpredictability-entropy $(Z^n, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  If $s_{sec} \geq t(|\rec|+n\log |Z|)$, then $\tilde{m}\leq n\log |Z| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
\end{theorem}
In particular, if the input is uniform, the entropy loss is about $\log |B_t(\cdot)|$.  Essentially the same entropy loss can be achieved with information-theoretic secure sketches, by using the code-offset construction\lnote{cite here, and is it the randomized construction or the deterministic one that we should use here?} applied to the best possible codes (e.g., random codes\lnote{cite performance of codes?}).  Thus, unpredictability-entropy secure sketches cannot improve on the best possible information-theoretic entropy loss (at least for uniform inputs).  However, because the best possible codes may not have efficient decoding, it is conceivable that unpredictability entropy secure sketch could achieve lower entropy loss than is possible with efficient information-theoretic sketches.

This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.  The main difference with \thref{thm:impSketchArbitraryW} is that it is unknown if the indistinguishable distribution contains many points.  This means we cannot construct a good code out of the points of $Y$.  \lnote{I find the previous three sentences more confusing than helpful; do we really need them?  should we reword or remove?} %Our bound is a result of the Hamming bound for the space.

@@

The lower bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} are strongest for high entropy sources.  The results get weaker as we consider sources with lower starter entropy.  This is necessary, if a source contains only codewords (of an error correcting code), no sketch is needed.  This means we cannot rule out computational sketches for other arbitrary lower entropy distributions.  This same situation occurs when considering lower bounds for information-theoretic sketches~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08} .

@@

In this section we describe our main construction.  In this section, we consider only a uniform source $W$, we consider other distributions in \secref{sec:LWE block fixing sources}.  Our construction uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.   Let $\decode_t$ be an algorithm that decodes a random linear code with at most $t$ errors.  We provide an informal description below.
%Please refer to \consref{cons:informal construction} for the description of the construction.

\begin{construction}
Let $n$ be a security parameter and let $m> n$.  %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
Define $\gen, \rep$ as follows:%The following construction is a computational secure sketch:
%Code-offset construction of a secure sketch using a random linear code over a finite field $\Fq$. $\decode_t (\vA, \vect{D})$ denotes an algorithm that decodes up to $t$ errors, i.e., an algorithm that finds $X'\in \Fq^n$ such that $\vect{A}X'$ is of Hamming distance at most $t$ from $\vect{D}$. $m > n$ are parameters to be figured out later.
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w\leftarrow W$ (where $W$ is some distribution over $\Fq^m$).
\item Sample $\vA\in\Fq^{m\times n}, X\in\Fq^n$ uniformly.
\item Compute $p = (\vA, \vA X+w)$, \\\ $r = X_{1,...,n/2}$.
\item Output $(r, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rec}
\begin{enumerate}
\item \underline{Input}: $(w', p)$ (where the Hamming distance between $w'$ and $w$ is at most $t$).
\item Parse $p$ as $(\vA, \vect{C})$; let $\vect{D}=\vect{C}-w'$.
\item Let $X = \decode_t(\vA, \vect{D})$\\
\item Output $r = X_{1,...,n/2}$.
\end{enumerate}
\end{minipage} 
\end{tabular}
\end{center}
\label{cons:informal construction}
\end{construction}

Intuitively, security comes from the computational hardness of decoding random linear codes from a high number of errors (introduced by $w$).  
In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $\delta^{\mathcal{D}_{s_{sec}}}((X_{1,..., n/2},P), (U_{n/2 \log q}, P))\leq \epsilon$.  Furthermore, this construction is only useful if $\decode_t$ can be efficiently implemented.  We demonstrate an efficient $\decode_t$ that corrects a super-polynomial number of error patterns in polynomial time.

@@

We cannot immediately adapt the construction in \consref{cons:informal construction} to the $\LWE$ problem.  Standard formulations of $\LWE$ require the error term to come from the discretized Gaussian distribution.  
%\subsection{LWE with uniform errors}
%\label{subsec:LWE uniform error}
Recent work D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the security of $\LWE$ with the uniform distribution over a small interval reduces to the security of $\LWE$ where the noise comes from the discretized Gaussian\footnote{Micciancio and Peikert provide a similar formulation in~\cite{micciancio2013hardness}.  The result D\"{o}ttling and M\"{u}ller-Quade provides better parameters for our setting.}.  This allows us to directly encode $w$ as the error term in an $\LWE$ problem by splitting it  into $m$ blocks.  The size of these blocks is dictated by the following result of D\"{o}ttling and M\"{u}ller-Quade:
%As stated above this has two advantages for Construction~\ref{cons:LWESecureSketch}: 1) the bits of $W$ can be used directly and \rep can output $w$ instead of $sam_w$ 2) there is a fixed number of bits required to sample each dimension.  
%We present the formulation of D\"{o}ttling and M\"{u}ller-Quade: 
%\begin{lemma}~\protect{~\cite[Theorem 5]{dottling2012}}
%\label{lem:uniform LWE}
%Let $n$ be a security parameter.  Let $q = q(n))$ and $m = m(n) = \poly(n)$ be integers.  Let $\rho = \rho(n) \in (0,1)$ be such that $\rho q\geq 2n^2m$.  Assume there exists a PPT-algorithm that solves the LWE decision problem where $\vA,X$ are drawn uniformly at random and $E$ is drawn from the interval $[-\rho q, \rho q]$ with non-negligible probability.  Then there exists an efficient quantum-algorithm that approximates the decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) to within $\tilde{O}(n^{5/2}m/\rho)$ in the worst case.
%\end{lemma}

%This problem can be stated in the language of indistinguishability using the Decision-to-search reduction of Regev or Peikert:
\begin{lemma}~\protect{~\cite[Corollary 10]{dottling2012}}
\label{lem:uniform LWE decision}
Let $n$ be a security parameter.  Let $q = q(n) = \poly(n)$ be a prime integer and $m = m(n) = \poly(n)$ be an integer. Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$. If the approximate decision-version of the shortest vector problem (GAPSVP) and the shortest independent vectors problem (SIVP) are hard~(on lattices of dimension $n/2$) within a factor of $\tilde{O}(n^{1/2+3\gamma}m/\rho)$ for quantum algorithms in the worst case, then, for $\chi$ the uniform distribution over $[-\rho q, \rho q]$, then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})\mbox{-}$secure, where $\epsilon = \ngl(n)$ for $s_{sec}=\poly(n)$.
\end{lemma}
